---
title: "p8105_hw1_xm2276"
author: "XIAO MA"
date: "9/29/2021"
output: github_document
---

---
title: "p8105_hw1_xm2276"
author: "XIAO MA"
date: "9/27/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Problem 1
```{r}
##Create a data frame
library(tidyverse)
example_df = tibble(
  vec_numeric = rnorm(10),
  vec_logical = vec_numeric > 0,
  vec_char = c("StudentA","StudentB","StudentC","StudentD","StudentE","StudentF","StudentG","StudentH","StudentI","StudentJ"),
  vec_factor = factor(c("Good","Good","Fair","Poor","Fair","Fair","Poor","Good","Poor","Fair"))
)

example_df
mean_examp_nu = mean(pull(example_df, vec_numeric))
mean_examp_nu
mean_examp_lo = mean(pull(example_df, vec_logical))
mean_examp_lo

```


##use the as.numeric function
```{r,eval=FALSE}
as.numeric(pull(example_df, vec_logical))
mean(as.numeric(pull(example_df, vec_logical)))
as.numeric(pull(example_df, vec_char))
mean(as.numeric(pull(example_df, vec_char)))
as.numeric(pull(example_df, vec_factor))
mean(as.numeric(pull(example_df, vec_factor)))

#After using `as.numeric`to logical, character, and factor variables, it helps us to find the mean on factor vectors. 
#The mean of logical variable changed from 0.6 to 1.9 since after using as.numeric the logical variable become only 1 or 0 (binary) hence the it is the mean of the binary result. 
#For character variable, it still cannot get the mean and the `as numeric` function does not work on charter variable. 
#For factor vectors, since it has three levels, by `as numeric` function it becomes to 1,2,3, and then mean is actually group of 1,2,3.
```



##problem2

```{r}
data("penguins", package = "palmerpenguins")
penguins
```

The**penguins** data set contains the following variable`r ls(penguins)`.
The number of rows of Penguin is `r nrow(penguins)`.
The number of columns of Penguin is `r ncol(penguins)`.
Flipper Length (mm) is a `r class(pull(penguins, flipper_length_mm))` variable. 
The mean of flipper length in mm is `r mean(pull(penguins, flipper_length_mm), na.rm=TRUE)`.



##Problem 2 scatterplot
```{r}

library(ggplot2)
ggplot(penguins) + geom_point(aes(bill_length_mm,flipper_length_mm,color = species))
ggsave("scatterplot_penguins.pdf")
```



